Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-08-26 paper.qmd
Updated Figure 17

error_plot_mnist <- error_df |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2, 
             color = type, 
             group = ID)) +
  geom_point(alpha=0.5, 
             size = 0.1) #+
  #interior_annotation("b", sc_ltr_pos_mnist)
```

@@

error_plot_mnist + 
  plot_layout(guides='collect') &
  theme(legend.position='bottom')
```

>>>>

error_plot_mnist <- error_df |>
  ggplot(aes(x = PaCMAP1,
             y = PaCMAP2, 
             color = type, 
             group = ID)) +
  geom_point(alpha=0.5, 
             size = 0.1) +
  scale_colour_brewer(
    type = "qual",
    palette = 2
  ) + 
    # Optional: Set a minimal theme
    theme(
        legend.position = "bottom",
        legend.text = element_text(size = 10),          # Increase legend text size
        legend.key.size = unit(1, "lines")              # Increase size of legend keys
    ) +
    guides(
        color = guide_legend(
            override.aes = list(size = 2.5, alpha = 1)      # Increase point size and opacity in legend
        )
    )
```

@@

error_plot_mnist 
```
